# Rating scale dataset

This document will go through a few open-source datasets and explain their characteristics

### Movielens 100K

Movielens is a non-commercial website that helps user find movies that they might like. It is run by GroupLens, a research lab at the University of Minnesota. Movielens datasets can be found on [Grouplens website](https://grouplens.org/datasets/movielens/). The 100K dataset has 100K observed values.

The 100K and the 1M are among those classified by Grouplens as "older datasets". The dataset they reccommend for new research is the 25M dataset from 2019, which is a lot more recent compared to the 100K dataset which is from 1998. Sadly, these datasets are too much for my hardware to handle so I cant visualise them like I did in this file.

```{r, fig.width=10, fig.height=11, echo=FALSE}
load("MovieLens100visuals.Rdata")
print(informationDf)
print(summary_plot)
```

### Movielens 1M

Movielens 1M also comes from Grouplens. It dates 2003, so it is slightly more recent than the 100K dataset. It constain 1M obserrvations.
```{r, fig.width=10, fig.height=11, echo=FALSE}
load("MovieLens1Mvisuals.Rdata")
print(informationDf)
print(summary_plot)
```

### Jester

Jester is a research project from the UC Berkeley Laboratory for Automation Science and Engineering. It is a joke reccomendation system, where users rate 100 jokes from  (-10.0 to 10). The datasets uses only user who have rated >35 jokes, although a different portion of the dataset is available for those that rated between 15 and 35 jokes. If you end up using this dataset email the owner out of courtesy.

For Jester, there are 4 datasets available.
```{r, fig.width=10, fig.height=11, echo=FALSE}
load("Jestervisuals.Rdata")
print(informationDf)
print(summary_plot)
```



